Seeing Double: Transient Dips and Photometric Binarity in PTFO$\,$8-8695

### 2020-04-21 paper/ms.tex
update paper

Between July 25, 2014 and May 23, 2016, Gaia measured about 300
billion centroid positions of 1{.}6 billion stars
\citep{gaia_collaboration_gaia_2016,lindegren_gaiasoln_2018,gaia_collaboration_gaia_2018}.
In the Gaia second data release (DR2), these CCD observations were
then used to estimate positions, proper motions, and parallax for the
brighest 1{.}3 billion stars, including \ptfo
\citep{lindegren_gaiasoln_2018}.  There were 121 ``good'' observations
of \ptfo, that is observations that were not strongly down-weighted in
its astrometric solution.  \ptfo\ was assigned a Gaia DR2 identifier
of 3222255959210123904.  It photometric brightness was measured using
selected bands ($G$, $Rp$, and $Bp$) of the Gaia Radial Velocity
Spectrometer \citep{cropper_gaia_2018,evans_gaia_2018}.  We accessed
the pipeline parameters for \ptfo\ using the Gaia
archive\footnote{\url{gea.esac.esa.int/archive/}}.

@@

\subsubsection{Cluster Membership}

The Orion molecular cloud complex has numerous subgroups, with ages
spanning 1 to 15$\,$Myr (CITE).
\ptfo\ has been known to be a member of the Orion OB1a association
since at least CITE (Briceno 2005).
Its relation to the broader Orion complex has been further explored by
CITEX, CITEY, and CITEZ (Briceno 05, 08, 18, whomever Van Eyken cites,
and Kounkel 18).

In describing the cluster membership of \ptfo, we follow the notation
and results of \citet{kounkel_apogee2_2018}.
\citet{kounkel_apogee2_2018} combined astrometric data from Gaia DR2
with spectroscopic data from APOGEE-2 (CITE).  They then performed a
hierarchical clustering on the six dimensional position and velocity
information to identify subgroups within the Orion complex.  From
smallest to largest groups, \ptfo\ was identified as being a member of
the following nested subgroups:
\begin{equation}
  %{\rm PTFO\,8\text{-}8695}
  % \in
  {\rm 25\,Ori\text{-}1}
  \subset {\rm 25\,Ori}
  \subset {\rm Orion\ OB1a}
  \subset {\rm Orion\ D},
\end{equation}
where from set-notation, `$\subset$' denotes ``is a proper subset of''.

While all members of the Orion complex are young relative to the
field, the internal age dispersion between different subgroups is
measurable.  The Orion Nebula Cluster (M42) is a site of ongoing
star-formation, and its stars are 1-3$\,$Myr old (CITE).
25$\,$Ori\-1, by contrast, is XX-XX$\,$Myr old (CITE).  These details
are essential when assessing any evidence for photometric binarity in
\ptfo, because there is a degeneracy between stellar luminosity and
age for stars on the pre-main-sequence.  Having a clean sample of
tightly spatially and kinematically associated stars is essential to
minimize contamination not just from the field, but from older and
younger members of the Orion complex itself.

@@

Our initial inspection of the lightcurve, in both its 2-minute PDCSAP
and 30-minute FFI forms, showed a strong sinusoidal beat signal
(Figure~\ref{fig:splitsignal}, top panel).

As a precursor to more detailed analysis, we calculated generalized
Lomb-Scargle periodograms using \texttt{astrobase}
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015,bhatti_astrobase_2018}.
The two largest peaks in the Lomb-Scargle periodogram of the
lightcurve were clearly separated at a ``short'' period $P_{\rm s}
\approx 0.448\,{\rm days}$ and a ``long'' period $P_{\rm \ell} \approx
0.499\,{\rm days}$.  The $P_{\rm \ell}$ peak had the greater power of
the two.  Smaller harmonics from each of these two dominants peaks
were also present.

@@

The peak-to-peak amplitude at maximum, when the two signals
constructively interfere, is about 14\%.  At minimum, the peak-to-peak
amplitude is about 6\%.  Assuming the signals are just two sinusoids,
algebra tells us that the peak-to-peak amplitudes should therefore be
10\% for the long-period signal, and 4\% for the short-period signal.
These order-of-magnitude numbers will turn out to be roughly correct.

@@

We opted to model the lightcurve as a linear combination of Fourier
harmonics at the short and long periods, plus a transit at the short
period.  Symbolically, the total flux $f$ is given as
\begin{equation}
  f = f_{\rm s} + f_{\rm \ell}
  = f_{\rm transit,s} + f_{\rm Fourier,s} + f_{\rm Fourier,\ell},
\end{equation}
where $f_{\rm s}$ is the relative flux at the short period, and
$f_{\rm \ell}$ is the flux at the long period.  Writing out the
Fourier terms,
\begin{align}
  f = &f_{\rm transit,s} + \sum_{n=1}^{N} A_n \sin(n\omega_{\rm s}t)
  + \sum_{n=1}^{N} B_n \cos(n\omega_{\rm s}t)\\
  &+ \sum_{m=1}^{M} A_m \sin(m[\omega_{\rm \ell}t+\phi_{\rm \ell}])
  + \sum_{m=1}^{M} B_m \cos(m[\omega_{\rm \ell}t+\phi_{\rm \ell}]), \nonumber
\end{align}
for $N$ and $M$ the total number of harmonics at the short and long
periods, respectively, $A_i$ and $B_i$ the amplitudes for each
harmonic term (potentially negative), and $\omega_i = 2\pi / P_i$ the
angular frequency for $i$ the short or long period index.  We fixed
the ``phase-offset'' for the short period signal to be zero, and let
the reference time for the long period signal float by introducing
$\phi_{\rm \ell}$.  Since we did not a priori know how many harmonics
would be appropriate, we considered a number of different choices for
$N$ and $M$, and used the Bayesian information criterion to choose the
appropriate model (Table~\ref{tab:modelcompare}).

As an example, one possible model could be a transit, plus $N=2$
harmonics of sines and cosines at the short period, plus $M=1$
harmonics at the long period.  In this case, the free parameters would
be as follows.  For the transit, we would fit for the impact
parameter, the planet-to-star radius ratio, two quadratic limb
darkening parameters, the planet orbital period (equal to the short
period), the reference time for the transit, and the mean flux.  There
would be $2N=4$ additional Fourier amplitudes at the short period,
plus $2M=2$ Fourier amplitudes at the long period, and well as the
long period itself and its phase.  For this case, we therefore fitted
14 free parameters.

We implemented and fitted the models using \texttt{PyMC3}, which is
built on \texttt{theano}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the Fourier terms,
we used the default math operators.  For the exoplanet transit, we
used the model and derivatives implemented in \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  Our priors are listed in
Table~\ref{tab:posterior}.  To speed up the fitting, we binned the
cleaned 2 minute lightcurves to 10 minute bins.  We correspondingly
scaled the uncertainties in the flux measurements by a factor of
$\sqrt{5}$.  Before sampling, we initialized each model to the maximum
a posteriori (MAP) solution.  We then sampled using \texttt{PyMC3}'s
gradient-based No-U-Turn Sampler \citep{hoffman_no-u-turn_2014}, and
used $\hat{R}$ as our convergence diagnostic
\citep{gelman_inference_1992}.
We tested our ability to successfully recover injected parameters
using synthetic data, before switching to the actual \ptfo\
lightcurves.

@@

We considered nine models, with the number of harmonics per frequency
$N$ and $M$ ranging from one to three.  To select our preferred model,
we used the Bayesian information criterion
(Table~\ref{tab:modelcompare}).  The model with the lowest BIC had
two harmonics at the short 10.74$\,$hr period, and two harmonics
at the long 11.96$\,$hr period.  All of the models have reduced
$\chi^2$ ranging between 1.37 and 1.51, which suggests a plausible
though imperfect agreement between the data and models.

@@

In every model, the variability at the long period is a simple
sinusoid with peak-to-peak amplitude $\approx$10\%.  The variability
at the short period is always more complex.  A dip of depth
$\approx$1.2\%, fit in our model as a transit, lasts $\approx$0.75
hours.  Superposed on the dip is a complex signal with peak-to-peak
amplitude of about 4\%, which peaks near phase 0.25, and reaches
minimum brightness between phases -0.5 and -0.25.

Outside of the primary dip, the short-period signal is relatively
smooth, at least from phases 0 to 0.5.  However the short-period
signal is asymmetric.  The flux from phases -0.5 to 0 shows what could
be a discontinuous jump, shortly after reaching minimum.  This jump
was visible in each of the nine models we considered.

@@

\subsection{Blend considerations}
\label{subsec:blend}

@@

The TESS pixels are $\approx21$'' per side, and so before making an
interptations, we need to consider whether light from neighboring
stars could have affected the photometry.  The scene is shown in
Figure~\ref{fig:scene}.  The pixels used to measure the background
level in the SPOC lightcuirve are indicated with an `\texttt{X}'
hatch, and the pixels used in the final lightcurve aperture are shown
with the `\texttt{/}' hatch.

The target star, \ptfo\ (TIC 264461976), has a $T$-band magnitude
of 14.0, and its position is shown with a star.  The other (unlabeled)
star inside the target aperture, TIC 264461979, has $T=16.8$ and so
cannot contribute a signal with relative amplitude 10\%.  The only
neighbor that is sufficiently close and bright that its light might
contaminate the target star is TIC 264461980, with $T=14.8$, which we
denote ``Star A''.  Star A is 23.6'' NW of our target, and based on
the magnitude difference could contribute up to 48\% the flux of our
target star, \ptfo.

Because \ptfo\ has previously been identified to have periodicity
consistent with our measurement of $P_{\rm s}$, our main concern
regarding blending is the degree to which we can be certain that the
long-period signal at $P_{\rm \ell}$ also originates from \ptfo.
We took two approaches towards determining the source of the
long-period signal.

First, we examined the CDIPS full frame image lightcurves of the
target, which are available on MAST \citep{bouma_cluster_2019}.  The
maximal peak-to-peak beat amplitude is consistently $\approx$10\%
across apertures of radii 1, 1.5, and 2.25 pixels.  If Star A were the
source of the long-period variability, we would expect the peak
variability amplitude to be smallest in the 1 pixel aperture, based on
the separation of the sources (Figure~\ref{fig:scene}, bottom).  From
this test alone, it seems unlikely that Star A is the source of the
long-period signal.

Second, we examined the lightcurve of each pixel in the scene
individually.  We opted to use the interactive tools implemented in
\texttt{lightkurve} \citep{lightkurve_2018}.  If Star A were the
source of the long-period variability, we would expect the pixels
nearest to Star A to show a sinusoidal signal with amplitude exceeding
$10\%$.  We find no evidence for this being the case.  The pixel
directly below Star A does not clearly show the sinusoidal
variability, and the peak-to-peak variability in that pixel is
$\lesssim 8\%$.  In contrast, the south-easternmost pixel within
\ptfo's aperture (the pixel furthest from Star A that was used in the
optimal aperture) shows the $P_{\rm \ell}$ sinusoidal variability
signal at $\approx 10\%$ amplitude.

As there is no evidence in favor of a blend scenario, we conclude that
both the $P_{\rm s}$ and $P_{\rm \ell}$ signals originate from \ptfo,
at least within the resolution of the Gaia-DR2 source catalog.
However, as we shall see, \ptfo itself could still be a binary.

\section{Gaia Analysis}
\label{sec:gaia}

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.9\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
%   Members of the 25$\,$Ori-1 subgroup are shown with black circles,
%   and were identified by \citet{kounkel_apogee2_2018} through
%   clustering on Gaia-DR2 and APOGEE data.  The ``neighborhood'' (gray
%   circles) is defined as the group of at most $10^4$ randomly selected
%   non-member stars within 5 standard deviations of the mean right
%   ascension, declination, and parallax.
% 	\label{fig:gaia}
% 	}
% \end{figure*}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		%\includegraphics[width=0.8\textwidth]{f5a.pdf}
    \subfloat{
        \includegraphics[width=0.7\textwidth]{f5a}
    }

	\vspace{-0.7cm}
    \subfloat{
        \includegraphics[width=0.7\textwidth]{f5b}
    }
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Evidence for binarity in \ptfo}.
  {\it Top: Hertzsprung-Russell diagram of \ptfo\ and late-type
  members of 25$\,$Ori-1.}
  Members of the 25$\,$Ori-1 group (black circles) were identified by
  \citet{kounkel_apogee2_2018} through clustering on six-dimensional
  Gaia-DR2 and APOGEE-2 data.  The ``neighborhood'' (gray
  circles) is non-member
  stars within 5 standard deviations of the mean 25$\,$Ori-1 right
  ascension, declination, and parallax.  It contains members of the
  Orion complex with its full spread of ages, in addition to field
  interlopers.  $G$ denotes Gaia broadband magnitudes, $Bp$ Gaia blue, $Rp$
  Gaia red, and $\omega_{\rm as}$ the parallax in arcseconds.  The
  $x$-axis limits have been set to show only K and M dwarf members, to
  accentuate \ptfo's separation from the single-star sequence.
  {\it Bottom: Astrometric goodness-of-fit versus $Rp$ magnitude
  for 25$\,$Ori-1 members}.
  The single-source astrometric model provides a poor fit, which
  could be due to stellar variability or binarity.
	\label{fig:gaia}
	}
\end{figure*}

%FIXME: summarize existant AO constraints here too
\citet{schmidt_direct_2016}
\citet{lee_evidence_2018}
% \citet{czesla_xray_2019}

\subsection{Photometric Binarity}
To assess the cluster membership and potential binarity of \ptfo, we
needed to identify stars with which it was and was not coeval.  The
simplest way to do this---clustering based on six-dimensional position
and kinematic information---had already been done by
\citet{kounkel_apogee2_2018}.  For simplicity, we considered the
members they identified brighter than $G_{\rm Rp}$ of 16.  This
yielded 149 stars in 25$\,$Ori-1, mostly M dwarfs.
\citet{kounkel_apogee2_2018} identified seven other smaller groups in
the Orion complex near the Be star 25$\,$Ori. These groups received
higher numbers, {\it e.g.}, 25$\,$Ori-2.

To define a set of non-member stars that nonetheless had comparable
selection functions, we defined a reference ``neighborhood'' as the
group of at most $10^4$ randomly selected non-member stars within 5
standard deviations of the mean 25$\,$Ori-1 right ascension,
declination, and parallax.  We queried these stars using the
\texttt{astroquery} package, which provides a convenient interface to
the Gaia archive (CITE, CITE).  This yielded 1{,}819 neighbors.  While
some of these stars may indeed be members of the Orion complex, or
even of 25$\,$Ori-1, enforcing this cut on positions and parallaxes
ensures that we are querying stars with comparable amounts of
interstellar reddening.

We examined the resulting five-dimensional right ascension,
declination, proper motions, and parallaxes.  The first point we noted
was that 25$\,$Ori-1 was a clearly defined over-density in each
dimension, so the cluster exists, and is different from the
neighborhood.  \ptfo\ was also clearly a member in each of these
projected dimensions.

Given our detection of two separate signals, whether \ptfo\ could be a
photometric binary was of great interest.  Figure~\ref{fig:gaia} shows
the HR diagram from which we assessed this issue.  The diagram shows
that \ptfo\ is $\approx$0.8 magnitudes brighter than the average
25$\,$Ori-1 star of the same color.  In other words, it is about twice
as bright.  It also seems to be on the photometric binary track of the
cluster, which has a few other stars.

The implication is that either {\it (i)} \ptfo\ is notably younger
than the kinematically identical cluster members, or {\it (ii)} \ptfo\
is a photometric binary.  Given the independent presence of two
resolved signals, we favor the interpretation that \ptfo\ is a binary
star system.

@@

As noted in Section~\ref{sec:observations}, the Gaia DR2 solution for
\ptfo\ shows a 10.3$\sigma$ astrometric excess.  This astrometric
excess indicates the degree to which a single-source model fails to
explain the observed astrometric measurements.  Specifically, the
single-source astrometric model for yielded $\chi^2=325.2$.  There
are 121 astrometric measurements, and 5 free parameters, and therefore
116 degrees of freedom. The reduced $\chi^2$ is 2.80.  The
majority of stars with comparable brightness in Gaia do not show such
poor goodness-of-fit \citep[][Appendix A]{lindegren_gaiasoln_2018}.

@@

The standard interpretation of sinusoidal modulations for a
pre-main-sequence M dwarf is that we are observing a stellar rotation
period of 11.96 hours.  This is the dominant signal in the system with
10\% amplitude, and there is no evidence to suggest that this signal
has any other origin.

>>>>

Between July 25, 2014 and May 23, 2016, Gaia measured about 300
billion centroid positions of 1{.}6 billion stars
\citep{gaia_collaboration_gaia_2016,lindegren_gaiasoln_2018,gaia_collaboration_gaia_2018}.
In the Gaia second data release (DR2), these CCD observations were
used to estimate positions, proper motions, and parallax for the
brighest 1{.}3 billion stars, including \ptfo\ 
\citep{lindegren_gaiasoln_2018}.  There were 121 ``good'' observations
of \ptfo, that is observations that were not strongly down-weighted in
its astrometric solution.  \ptfo\ was assigned a Gaia DR2 identifier
of 3222255959210123904.  It photometric brightness was measured using
selected bands ($G$, $Rp$, and $Bp$) of the Gaia Radial Velocity
Spectrometer \citep{cropper_gaia_2018,evans_gaia_2018}.  We accessed
the pipeline parameters for \ptfo\ using the Gaia
archive\footnote{\url{gea.esac.esa.int/archive/}}.

@@

\subsubsection{Hierarchical Cluster Membership}
\label{subsec:hierarchical}

Gaia also provided astrometric parameters for tens of thousands of
young stars in the Orion complex.  The stellar populations in giant
molecular cloud complexes are not monolithic; substructured groups are
the norm \citep{briceno_lowmassOB_2007}.  The Orion molecular cloud
complex in particular has numerous subgroups, with ages spanning 0.5
to 15$\,$Myr. For an incomplete sampling, see for instance
\citet{briceno_cida_2005,jeffries_kinematic_2006,briceno_25_2007,kounkel_apogee2_2018}
and \citet{briceno_cidaII_2019}.

\ptfo\ was initially identified as a member of the Orion$\,$OB1a
sub-association by \citet{briceno_cida_2005} through combined
photometry and spectroscopy.  Later work by \citet{briceno_25_2007}
clarified that \ptfo\ was in a kinematically distinct subgroup of
Orion~OB1a, named the ``25$\,$Ori'' group after its brightest
member. The 25$\,$Ori group had an isochrone age of 7--10$\,$Myr, and
had a smaller disk fraction than younger nearby sub-associations
\citep{hernandez_spitzer_2007}.

With the Gaia astrometry, it has become clear that 25$\,$Ori itself
has further subgroups
\citep{kounkel_apogee2_2018,briceno_cidaII_2019}.  In describing the
cluster membership of \ptfo, we follow the notation and results of
\citet{kounkel_apogee2_2018}.  These authors combined astrometric data
from Gaia DR2 with near-infrared spectra from APOGEE-2
\citep{gunn_sdss_2006,majewski_apache_2017,blanton_sloan_2017,zasowski_target_2017,cottle_apogee2_2018}.
They performed a hierarchical clustering on the six dimensional
position and velocity information to identify subgroups within the
Orion complex.  From smallest to largest, \ptfo\ was identified
as being a member of the following hierarchical subgroups:
\begin{equation}
  %{\rm PTFO\,8\text{-}8695}
  % \in
  {\rm 25\,Ori\text{-}1}
  \subset {\rm 25\,Ori}
  \subset {\rm Orion\ OB1a}
  \subset {\rm Orion\ D},
\end{equation}
where from set-notation, `$\subset$' denotes ``is a proper subset of''.
25$\,$Ori-1 is the largest subgroup of 25$\,$Ori, with 149 identified
members.
Its mean age from its CMD was found to be 6.9$\,$Myr, and from its HR
diagram 8.5$\,$Myr \citep{kounkel_apogee2_2018}.
\citet{kounkel_apogee2_2018} identified seven other smaller groups in
the Orion complex near the Be star 25$\,$Ori. These groups received
higher numbers, {\it e.g.}, 25$\,$Ori-2 (${\rm Age}_{\rm CMD} =15.1\,$Myr; ${\rm Age}_{\rm CMD} =12.9\,$Myr; see also \citealt{briceno_cidaII_2019}).

These details concerning the group membership for one object may seem
cumbersome to those accustomed to comparing ``young cluster
members'' with ``old field stars''.  Though all members of the Orion
complex are indeed young relative to the field, these details are
essential for assessing any evidence for photometric binarity in
\ptfo, because of the degeneracy between stellar luminosity and
age for pre-main-sequence stars.  Having a clean sample of tightly
spatially and kinematically associated reference stars
minimizes contamination not just from the field, but from older and
younger members of the Orion complex itself.

@@

Our initial inspection of the TESS lightcurve, in both its 2-minute PDCSAP
and 30-minute FFI forms, showed a strong sinusoidal beat signal
(Figures~\ref{fig:splitsignal} and~\ref{fig:splitsignalii}, top panel).

As a precursor to more detailed analysis, we calculated generalized
Lomb-Scargle periodograms using \texttt{astrobase}
\citep{lomb_1976,scargle_studies_1982,vanderplas_periodograms_2015,bhatti_astrobase_2018}.
The two largest peaks in the Lomb-Scargle periodogram of the
lightcurve were clearly separated at a ``short'' period $P_{\rm s}
\approx 0.448\,{\rm days}$ and a ``long'' period $P_{\rm \ell} \approx
0.499\,{\rm days}$.  The $P_{\rm \ell}$ peak had the greater power of
the two.  Smaller harmonics surrounding each of these two dominants peaks
were also present.

@@

The peak-to-peak lightcurve amplitude at maximum, when the two signals
constructively interfere, is about 14\%.  At minimum, the peak-to-peak
amplitude is about 6\%.  Assuming the signals are just two sinusoids,
algebra tells us that the peak-to-peak amplitudes should therefore be
10\% for the long-period signal, and 4\% for the short-period signal.
These order-of-magnitude numbers will turn out to be roughly correct.

@@

We fitted the lightcurve as a linear combination of Fourier
harmonics at the short and long periods, plus a transit at the short
period.  Symbolically, the total flux $f$ is given as
\begin{equation}
  f = f_{\rm s} + f_{\rm \ell}
  = f_{\rm transit,s} + f_{\rm Fourier,s} + f_{\rm Fourier,\ell},
\end{equation}
where $f_{\rm s}$ is the relative flux at the short period, and
$f_{\rm \ell}$ is the flux at the long period.  Writing out the
Fourier terms,
\begin{align}
  f = &f_{\rm transit,s} + \sum_{n=1}^{N} A_n \sin(n\omega_{\rm s}t)
  + \sum_{n=1}^{N} B_n \cos(n\omega_{\rm s}t)\\
  &+ \sum_{m=1}^{M} A_m \sin(m[\omega_{\rm \ell}t+\phi_{\rm \ell}])
  + \sum_{m=1}^{M} B_m \cos(m[\omega_{\rm \ell}t+\phi_{\rm \ell}]), \nonumber
\end{align}
for $N$ and $M$ the total number of harmonics at the short and long
periods, respectively, $A_i$ and $B_i$ the amplitudes for each
harmonic term (potentially negative), and $\omega_i = 2\pi / P_i$ the
angular frequency for $i$ the short or long period index.  We fixed
the ``phase-offset'' for the short period signal to be zero, and let
the reference time for the long period signal float by introducing
$\phi_{\rm \ell}$.  Since we did not a priori know how many harmonics
would be appropriate, we considered a number of different choices for
$N$ and $M$, and used the Bayesian information criterion to choose the
appropriate model (Table~1).

As an example, one possible model could be a transit, plus $N=2$
harmonics of sines and cosines at the short period, plus $M=1$
harmonics at the long period.  For this case the free parameters would
be as follows.  For the transit, we would fit for the impact
parameter, the planet-to-star radius ratio, two quadratic limb
darkening parameters, the planet orbital period (equal to the short
period), the reference time for the transit, and the mean flux.  There
would be $2N=4$ additional Fourier amplitudes at the short period,
plus $2M=2$ Fourier amplitudes at the long period, and well as the
long period itself and its phase.  For this case, we therefore fitted
14 free parameters.

We implemented and fitted the models using \texttt{PyMC3}, which is
built on \texttt{theano}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  For the Fourier terms,
we used the default math operators.  For the exoplanet transit, we
used the model and derivatives implemented in \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  Our priors are listed in
Table~2.  To speed up the fitting, we re-sampled the
cleaned 2 minute lightcurves to 10 minute binning.  We correspondingly
scaled the uncertainties in the flux measurements by a factor of
$\sqrt{5}$.  Before sampling, we initialized each model to the maximum
a posteriori (MAP) solution.  We then sampled using \texttt{PyMC3}'s
gradient-based No-U-Turn Sampler \citep{hoffman_no-u-turn_2014}, and
used $\hat{R}$ as our convergence diagnostic
\citep{gelman_inference_1992}.
We tested our ability to successfully recover injected parameters
using synthetic data, before fitting the \ptfo\
lightcurves.

@@

We considered nine models, with the number of harmonics per frequency
$N$ and $M$ ranging from one to three.  To select our preferred model,
we used the Bayesian information criterion
(Table~1).  The model with the lowest BIC had
two harmonics at the short 10.74$\,$hr period, and two harmonics
at the long 11.96$\,$hr period.  
The next-best model had an additional harmonic at the longer period ($M=3$),
but was otherwise identical.
All nine models have reduced
$\chi^2$ ranging between 1.37 and 1.51, which suggests a plausible
though imperfect agreement between the data and fitting results.
The best-fit parameters for the lowest BIC model are given in Table~2.

@@

In every model, the $11.96\,{\rm hr}$ variability is a simple
sinusoid with peak-to-peak amplitude $\approx$10\%.  The $10.74\,{\rm hr}$ variability
is always more complex.  A dip of depth
$\approx$1.2\%, fit in our model as a transit, lasts $\approx$0.75
hours.  Superposed on the dip is a slightly asymmetric sinusoid with peak-to-peak
amplitude of about 4\%. The asymmetric sinusoid peaks near phase 0.25, and reaches
minimum brightness between phases -0.5 and -0.25.
The flux at phase $\approx -0.33$ shows what could
be a discontinuous jump, shortly after reaching minimum (Figure~\ref{fig:phasefold}).  This jump
was visible in each of the nine models we considered.

@@

\section{Binarity Analysis}
\label{sec:gaia}

% \begin{figure*}[t]
% 	\begin{center}
% 		\leavevmode
% 		\includegraphics[width=0.9\textwidth]{f6.png}
% 	\end{center}
% 	\vspace{-0.7cm}
% 	\caption{ {\bf Positions, kinematics, and HR diagram of \ptfo.}
%   Members of the 25$\,$Ori-1 subgroup are shown with black circles,
%   and were identified by \citet{kounkel_apogee2_2018} through
%   clustering on Gaia DR2 and APOGEE data.  The ``neighborhood'' (gray
%   circles) is defined as the group of at most $10^4$ randomly selected
%   non-member stars within 5 standard deviations of the mean right
%   ascension, declination, and parallax.
% 	\label{fig:gaia}
% 	}
% \end{figure*}

\subsection{Visual Binarity}
\label{subsec:blend}

@@

The TESS pixels are $\approx21$'' per side. Before making any
interpretations, we needed to consider whether light from known neighboring
stars could have affected the photometry.  The scene is shown in
Figure~\ref{fig:scene}.  
In the upper panels, the pixels used to measure the background
level in the SPOC lightcurve are indicated with an `\texttt{X}'
hatch, and the pixels used in the final lightcurve aperture are shown
with the `\texttt{/}' hatch.

The target star, \ptfo\ (TIC 264461976), has a $T$-band magnitude
of 14.0, and its position is shown with a star.  The other (unlabeled)
star inside the target aperture, TIC 264461979, has $T=16.8$ and so
cannot contribute a signal with relative amplitude 10\%.  The only
neighbor that is sufficiently close and bright that its light might
contaminate the target star is TIC 264461980, with $T=14.8$, which we
dub ``Star A''.  Star A is 23.6'' NW of our target, and based on
the magnitude difference could contribute up to 48\% the flux of our
target star, \ptfo.

Because \ptfo\ was previously identified to have periodicity
consistent with our measurement of $P_{\rm s}$, our main concern
regarding blending was the degree to which we could be certain that the
long-period signal at $P_{\rm \ell}$ also originated from \ptfo.
We took two approaches to verifying the source of the
long-period signal.

First, we examined the CDIPS FFI lightcurves of the
target, which were available on MAST \citep{bouma_cluster_2019}.  The
maximal peak-to-peak beat amplitude was constant
across apertures of radii 1, 1.5, and 2.25 pixels to visual precision ($\lesssim 1\%$).
If Star A were the
source of the long-period variability, we would expect the peak
variability amplitude to be smallest in the 1 pixel aperture, based on
the separation of the sources (Figure~\ref{fig:scene}, bottom).  From
this test alone, it seems unlikely that Star A is the source of the
long-period signal.

Second, we examined the 2-minute lightcurve of each pixel in the scene
individually.  We opted to use the interactive tools implemented in
\texttt{lightkurve} \citep{lightkurve_2018}.  If Star A were the
source of the long-period variability, we would expect the pixels
nearest to Star A to show a sinusoidal signal with amplitude exceeding
$10\%$.  The data do not support this possibility.  The pixel
directly below Star A does not clearly show the sinusoidal
variability, and the peak-to-peak variability in that pixel is
$\lesssim 8\%$.  In contrast, the south-easternmost pixel within
\ptfo's aperture (the pixel furthest from Star A that was used in the
optimal aperture) shows the $P_{\rm \ell}$ sinusoidal variability
signal at $\approx 14\%$ amplitude.
We conclude that
within the resolution of the Gaia DR2 source catalog,
the $P_{\rm s}$ and $P_{\rm \ell}$ signals originate from \ptfo.
From \citet{ziegler_measuring_2018}, we can surmise that
stellar companions
wider than $\approx$1'' (349~AU) and within
$\Delta G \approx 3$ magnitudes of \ptfo\ would have likely been
detected through this approach.

\citet{van_eyken_ptf_2012} obtained
stronger constraints on possible stellar companions using the
NIRC2 camera on Keck II.
They reported 3$\sigma$ $H$-band magnitude difference limits
of 4.3, 6.4, and 8.9 at angular separations of 0.25, 0.5, and 1.0
arcseconds (87, 175, and 349~AU).
They also detected a point-source, not present in Gaia DR2,
7.0 magnitudes fainter than the target, 
and 1.8$''$ north-east.
Due to the brightness difference, this coincident star\footnote{This companion was claimed to be a potential planetary-mass
	object \citep{schmidt_direct_2016}. Subsequent analysis of its colors showed that it is
	a background star \citep{lee_evidence_2018}.} cannot be the source
of our signals.

%FIXME: would be better to actually be able to get them...
While long-baseline radial velocity measurements could provide complimentary
lower limits on companion masses and separations, the RV
data for \ptfo\ are rather poor owing to the stellar faintness.
The longest single-instrument baseline in the literature appears to be 5 Keck/HIRES
measurements acquired over 10 days in April 2011 by \citet{van_eyken_ptf_2012}.
The RV RMS over that 10 day span was $1.6\,{\rm km}\,{\rm s}^{-1}$, consistent with
the measurement precision.
Though \citet{yu_tests_2015} acquired 22 further Keck/HIRES observations over
one night in December 2013, these points seem to not have been
reduced to velocities.
Further Keck/HIRES measurements of this target could confirm or
refute the existence of possible binary companions.

\subsection{Photometric Binarity}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f5a.pdf}
		}

		\vspace{-0.7cm}
		\subfloat{
			\includegraphics[width=0.7\textwidth]{f5b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Evidence for binarity in \ptfo}.
		{\it Top: Hertzsprung-Russell diagram of \ptfo\ and late-type
			members of 25$\,$Ori-1.}
		Members of the 25$\,$Ori-1 group (black circles) were identified by
		\citet{kounkel_apogee2_2018} through clustering on six-dimensional
		Gaia DR2 and APOGEE-2 data.  The ``neighborhood'' (gray
		circles) is non-member
		stars within 5 standard deviations of the mean 25$\,$Ori-1 right
		ascension, declination, and parallax.  It contains members of the
		Orion complex with its full spread of ages, in addition to field
		interlopers.  $G$ denotes Gaia broadband magnitudes, $Bp$ Gaia blue, $Rp$
		Gaia red, and $\omega_{\rm as}$ the parallax in arcseconds.  The
		$x$-axis limits have been set to show only K and M dwarf members, to
		accentuate \ptfo's separation from the single-star sequence.
		{\it Bottom: Astrometric goodness-of-fit versus $Rp$ magnitude
			for 25$\,$Ori-1 members}.
		The single-source astrometric model provides a poor fit, which
		could be due to stellar variability or binarity.
		\label{fig:gaia}
	}
\end{figure*}

Aside from visual binarity, we can also check the Gaia data
for photometric binarity.
To assemble a set of stars coeval with \ptfo,
we used the 25$\,$Ori-1 members identified by
\citet{kounkel_apogee2_2018}, and discussed in Section~\ref{subsec:hierarchical}.

To define a set of non-member stars that nonetheless had comparable
selection functions, we defined a reference ``neighborhood'' as the
group of at most $10^4$ randomly selected non-member stars within 5
standard deviations of the mean 25$\,$Ori-1 right ascension,
declination, and parallax.  We queried Gaia DR2 for these stars using
\texttt{astroquery} \citep{astroquery_2018}.  This yielded 1{,}819 neighbors.  While
some of these stars may indeed be members of the Orion complex, or
even of 25$\,$Ori-1, enforcing this cut on positions and parallaxes
ensures that we are querying stars with comparable amounts of
interstellar reddening.

We examined the resulting five-dimensional right ascension,
declination, proper motions, and parallaxes.  The first point we noted
was that 25$\,$Ori-1 was a clearly defined over-density in each
dimension---the cluster exists, and is distinct from the
neighborhood.  \ptfo\ was also within the cluster in each of these
projected dimensions.

Given our detection of two separate signals, whether \ptfo\ could be a
photometric binary was of great interest.  Figure~\ref{fig:gaia} shows
the HR diagram we constructed to assess this issue.  The diagram shows
that \ptfo\ is $\approx$0.75 magnitudes brighter than the average
25$\,$Ori-1 star of the same color.  In other words, it is about twice
as bright.  It also seems to be coincident with the photometric binary track of the
cluster, which has a few other stars.

The implication is that either {\it (i)} \ptfo\ is notably younger
than the kinematically identical 25$\,$Ori-1 members, or {\it (ii)} \ptfo\
is a photometric binary.
Since there is no a priori reason to suspect an age difference,
but we have resolved two
separate photometric signals, we favor the binary interpretation.

@@

A separate possible line of evidence for binarity is the Gaia DR2 astrometry.
As noted in Section~\ref{sec:observations}, the Gaia DR2 solution for
\ptfo\ shows a 10.3$\sigma$ astrometric excess.  This astrometric
excess indicates the degree to which a single-source model fails to
explain the observed astrometric measurements.  Specifically, the
single-source astrometric model yielded $\chi^2=325.2$.  There
are 121 astrometric measurements, and 5 free parameters, and therefore
116 degrees of freedom. The reduced $\chi^2$ is 2.80.  The
majority of stars with comparable brightness in Gaia do not show such
poor goodness-of-fit \citep[][Appendix A]{lindegren_gaiasoln_2018}.

@@

The standard interpretation for 11.96$\,$hour sinusoidal modulations of a
pre-main-sequence M dwarf is stellar rotation.  This is the dominant signal in the system with
10\% amplitude, and there is no evidence to suggest that this signal
has any other origin.
